%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Weedmaps} % Organization
    {Remote} % Location
    {Aug. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Incremental migration from AngularJS to React + Next.js}
        \item {Led adoption of Typescript in a large codebase}
        \item {Implemented Cypress-based integration testing}
        \item {Worked to improve our CI/CD pipeline and into a gitops flow}
      \end{cvitems}
    }
 
%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {SpinGo} % Organization
    {Remote} % Location
    {Jan. 2012 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {AWS Infrastructure setup and management with SaltStack.}
        \item {Transitioned a monolithic PHP application to scalable Scala microservices with AngularJS and React / Redux client side}
        \item {Data integration with Salesforce}
        \item {Swift-based iOS app development (live in the AppStore)}
        \item {ETL Pipeline for data analysis using Vertica and Tableau}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Contract / Passion Projects} % Organization
    {Remote} % Location
    {Aug. 2012 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Android and iOS app using React Native and Redux (\href{http://wevyte.com}{WeVyte})}
        \item {Local business website development (\href{http://beyondbread.com}{Beyond Bread})}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Developer} % Job title
    {Raytheon Missile Systems} % Organization
    {Tucson, AZ} % Location
    {Dec. 2007 - Aug. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Front end web development for both raytheon.com and internal intranet}
        \item {Implemented JavaScript components and plugins integrated into Oracle CMS}
        \item {Led the migration away from Flash to modern and open web technologies}
        \item {Built the company’s first mobile and responsive microsites}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Director} % Job title
    {Spin Media Marketing} % Organization
    {Provo, UT} % Location
    {Jun. 2006 - Aug. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead developer for many internal and client web applications}
        \item {Ruby on Rails, Wordpress and Drupal development}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Audio Engineer} % Job title
    {Soularium Studios} % Organization
    {Alpine, UT} % Location
    {Dec. 2005 - Dec. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Audio recording, mixing, and mastering on a high-end Pro Tools DAW}
        \item {Troubleshooting and maintenance of studio computers and equipment}
        \item {Serving and hosting created audio to clients across the world}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Administrator} % Job title
    {BYU Media Arts Lab} % Organization
    {Provo, UT} % Location
    {Jan. 2004 - Dec. 2005} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed audio and video editing workstations}
        \item {Deployed a web-based equipment checkout system}
        \item {Trained students on industry-standard software}
        \item {Set up and maintained an Xgrid/Xserve system for streamlining media workflows}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
